\texttt{\Large{pyannote.metrics}}: a toolkit for reproducible evaluation,\\ diagnostic, and error analysis of speaker diarization systems

### 2017-03-17 paper.tex
improve: comments by Claude

Thanks to open initiatives such as the series of NIST ``Rich Transcription'' evaluations~\cite{Fiscus2006}, or ESTER~\cite{Galliano2005} and  ETAPE~\cite{Gravier2012} benchmarks, the state-of-the-art for speaker diarization has achieved significant improvement since 2000.
Despite addressing the same task, these initiatives used different evaluation metrics, different implementations of these metrics~\cite{NIST-RT03, Galibert2013}, all provided as standalone (C or Lua) command line tools.

In this paper, we introduce \metrics{}, an open-source Python library for reproducible evaluation, diagnostic, and error analysis of speaker diarization systems.
Python is currently being adopted by a growing number of researchers in speaker identification~\cite{sidekit, Bob2012}, machine learning~\cite{scikit-learn}, or deep learning~\cite{tensorflow2015-whitepaper}.
Being able to directly evaluate speaker diarization using the computer language in which systems are developed is therefore very convenient.

@@

As introduced in Section~\ref{sec:reproducible_evaluation}, \metrics{} can be used as a command line tool to compute the \emph{de facto} standard \emph{diarization error rate} NIST implementation.
Inspired by Bob~\cite{Bob2012} database package paradigm, \metrics{} rely on standardized database interfaces to ensure reproducibility and fair comparison of speaker diarization systems.
It also provides a large collections of additional evaluation metrics (summarized in Figure~\ref{fig:pipeline}) that can be used for diagnostic purposes, either using the command line tool, or directly as a Python module.
Those additional metrics are described, discussed, and compared in Section~\ref{sec:diagnostic}.
Finally, another strength of \metrics{} lies in its advanced visualization and error analysis features.
This is introduced in Section~\ref{sec:visualization}.

>>>>

Thanks to open initiatives such as the series of NIST ``Rich Transcription'' evaluations~\cite{Fiscus2006}, or ESTER~\cite{Galliano2005} and  ETAPE~\cite{Gravier2012} benchmarks, the state-of-the-art for speaker diarization has achieved significant improvement since 2000.
Despite addressing the same task, these initiatives used different evaluation metrics, different implementations of these metrics~\cite{NIST-RT03, Galibert2013}, all provided as standalone (Perl or Lua) command line tools.

In this paper, we introduce \metrics{}, an open-source Python library for reproducible evaluation, diagnostic, and error analysis of speaker diarization systems.
Python is currently being adopted by a growing number of researchers in speaker identification~\cite{sidekit, Bob2012}, machine learning~\cite{scikit-learn}, or deep learning~\cite{tensorflow2015-whitepaper}.
Evaluating speaker diarization using the same language as the one used for developing, training, and testing a system has several advantages.
In particular, it may be very convenient when the actual evaluation metric serves as a cost function to minimize during training.

@@

For the sake of completeness, \metrics{} can also be used as a command line tool (described in Section~\ref{sec:reproducible_evaluation}) to compute the \emph{de facto} standard \emph{diarization error rate} NIST implementation.
Inspired by Bob~\cite{Bob2012} database package paradigm, \metrics{} rely on standardized database interfaces to ensure reproducibility and fair comparison of speaker diarization systems.
It also provides a large collections of additional evaluation metrics (summarized in Figure~\ref{fig:pipeline}) that can be used for diagnostic purposes, either using the command line tool, or directly as a Python module.
Those additional metrics are described, discussed, and compared in Section~\ref{sec:diagnostic}.
Finally, another strength of \metrics{} lies in its advanced visualization and error analysis features.
This is introduced in Section~\ref{sec:visualization}.
